MATH/COMP 562 ASSIGNMENT 2

### 2023-06-29 assignment-2/article.tex
Solve 1.2

\subsection*{Exercise 1.2}
Given a hypothesis class $H$, of functions $h : X \rightarrow \mathbb{R}$, and a dataset $S = \{x_1 , \ldots, x_m\} \subset X$. Define $\Phi(S) = \sup_{h\in H} |E[h] - \hat{E}_S[h]|$ to be the least upper bound for the generalization gap of a function in $H$. Prove that $\hat{E}_S [\Phi(S)] \leq 2\hat{R}_m(H)$.

\subsection*{Exercise 1.3 (Rademacher Identities)}
Mohri 3.8(a) and 3.8(b).

>>>>

\begin{problem}{Exercise 1.2}
Given a hypothesis class $\mathcal{H}$, of functions $h : X \rightarrow \mathbb{R}$, and a dataset $S = \{x_1 , \ldots, x_m\} \subset X$. Define $\Phi(S) = \sup_{h\in \mathcal{H}} |\mathbb{E}[h] - \hat{\mathbb{E}}_S[h]|$ to be the least upper bound for the generalization gap of a function in $\mathcal{H}$.

Prove that $\hat{E}_S [\Phi(S)] \leq 2\hat{\mathfrak{R}}_m(\mathcal{H})$.
\end{problem}
